Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-15 ms.tex
reiterate that 100, 143 GHz two-component predictions shown are indeed extrapolations

\section{Low-frequency Emission Predictions}
\label{sec:lofreq}
FDS99 originally performed their \PLANCK+DIRBE dust SED analysis for the sake 
of accurately forecasting low-frequency CMB foregrounds. Recently, Galactic CMB
foregrounds, especially in the 100-150 GHz frequency range, have become a focal
point of cosmology owing to the \cite{bicep2} $B$-mode polarization results. 
Here we show that our two-component foreground predictions are more accurate 
than those based on the \cite{planckdust} single-MBB model over the 100-217 GHz
frequency range.

\begin{figure*}
\begin{center}
\epsfig{file=compare_lofreq.eps, width=6.8in}
\caption{\label{fig:lofreq} Comparison between low-frequency thermal dust 
emission predictions from our best-fit two-component model (Table 
\ref{tab:global}, model 2) and those of \cite{planckdust}. The top row shows
scatterplots of the \cite{planckdust} predictions versus observed \PLANCK~100 
GHz (left), \PLANCK~143 GHz (center) and \PLANCK~217 GHz (right). The bottom 
row shows scatterplots of the corresponding two-component predictions versus
\PLANCK~observations. In all cases, the blue line indicates the best-fit linear
relationship, while the red line represents a perfect match between predictions
and observations. The lines of best-fit illustrate that the single-MBB model 
systematically underpredicts emission (in the multiplicative sense) by 18.8\%, 
12.6\% and 7.9\% at 100, 143 and 217 GHz respectively. On the other hand, by 
the same metric, the two-component model predictions at 100-217 GHz are always 
accurate to within $\le$2.2\%.}
\end{center}
\end{figure*}

>>>>

\section{Low-frequency Emission Predictions}
\label{sec:lofreq}
FDS99 originally performed their FIRAS+DIRBE dust SED analysis for the sake of
accurately forecasting low-frequency CMB foregrounds. Recently, Galactic CMB
foregrounds, especially in the 100-150 GHz frequency range, have become a focal
point of cosmology owing to the \cite{bicep2} $B$-mode polarization results. 
Here we show that our two-component foreground predictions are more accurate 
than those based on the \cite{planckdust} single-MBB model over the 100-217 GHz
frequency range.

\begin{figure*}
\begin{center}
\epsfig{file=compare_lofreq.eps, width=6.8in}
\caption{\label{fig:lofreq} Comparison between low-frequency thermal dust 
emission predictions from our best-fit two-component model (Table 
\ref{tab:global}, model 2) and those of \cite{planckdust}. The top row shows
scatterplots of the \cite{planckdust} predictions versus observed \PLANCK~100 
GHz (left), \PLANCK~143 GHz (center) and \PLANCK~217 GHz (right). The bottom 
row shows scatterplots of the corresponding two-component predictions versus
\PLANCK~observations. In all cases, the blue line indicates the best-fit linear
relationship, while the red line represents a perfect match between predictions
and observations. The lines of best-fit illustrate that the single-MBB model 
systematically underpredicts emission (in the multiplicative sense) by 18.8\%, 
12.6\% and 7.9\% at 100, 143 and 217 GHz respectively. On the other hand, by 
the same metric, the two-component model predictions at 100-217 GHz are always 
accurate to within $\le$2.2\%. The two-component fit results shown are based on
217-3000 GHz observations, meaning that the 100 GHz and 143 GHz predictions are
truly extrapolations, while the 217 GHz agreement is enforced by the fitting 
process itself to some extent.}
\end{center}
\end{figure*}
